Appendix

### 2020-10-29 manuscript/bef_stability/appendix.Rmd
Manuscript update: colin rreview + new table and figures
Improve appendix clarity

library(tidyverse)
library(magrittr)
library(ggeffects)
library(cowplot)
library(kableExtra)
library(sf)
source(mypath("R", "misc.R"))
source(mypath("R", "plot_methods.R"))
source(mypath("R", "community_analysis.R"))
source(mypath("R", "community_methods.R"))
source(mypath("R", "statistical_analysis.R"))
source(mypath("R", "total_sem_effect.R"))
source(mypath("R", "press_methods.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "synchrony.R"))

@@

```{r, echo = FALSE}
package <- c("openSTARS", "SSN", "nlme", "piecewiseSEM")
purrr::map(package, ~ toBibtex(citation(.x)))

toBibtex(citation())

@@

The fish community sampling took place in a variety of stream size, shape and
depth. This diversity constraints the type of protocol that can take place.  For
the small streams (depth < 0.7m across the entire width), the complete protocol
is used. It consists in placing anodes every X meter across the width of the
river. The fishermen made from one to three row
of fishing. We kept only the first row for analysis to homogenize the sampling
effort. For deeper and wider streams, the sampling was partial over the bank and
the channel and performed by boat and by foot (along the bank). We kept only
sampling done over the bank because channel sampling was not always done.  Two
types of partial protocols takes place: partial over bank and partial by points.
The former is continuous while the latter is discrete. Furthermore, in partial
by point protocol the channel can be sampled as well. We kept only the partial
by point fish sampling which all the sampling point were done over the bank to
homogenize the sampling.  Then, we merged partial over bank and partial over
point protocols. Some sampling stations had mix characteristics in which mix of
partial and complete protocols were applied depending of the depth of the river
at the time of sampling. Those stations were removed from the analysis.

Heterogeneity in the sampling period may introduce variability that is not related
to ecological processes such as the presence of juveniles. In order to reduce
heterogeneity in sampling time, only one sampling per year was retained if there
was two in a given year, the one with with the most species and then individual
collected. Finally, most of the fish sampling occurred in September (Median:
mid-August) and the median standard deviation of the sampling month was inferior
to one (0.7) within station. Additionally, we removed sampling events, in a
given station, which the sampled length along the stream was outside the median
length sampled more or less 30%. Finally, we standardadized the biomass record
and species richness by the sampled surface to get rid of sampling effort
effects.

@@

During the electric fishing, and before that fish body size are measured, they
are regrouped by batches. Each batches contains one species but there can be
several batches by species. Body size assessment are different according to the
batches. There are four types of batches: N, I, S/L and G. The batches N and
I contains the biggest individuals, there are normally less numerous and then
the body size of the individuals of those batches is recorded. The batches S/L
contains fishes of intermediate sizes. Inside each S/L batches, the operator
tries to make batches as homogeneous as possible in body size. Then, the body
size of a subsample of X individuals are recorded. The G batches contain
individuals of low body size, with care that body size is as homogenous as
possible in the batches. Then body size of the shortest and the longest
individuals are recorded.

@@

```{r}
body_size_caption <- paste0(
  "Body size inference of the fishes. ",
  "(1) Sampled fishes were attributed to batch type according to their size and
  the number of individuals. A batch contains one species only. (2) In the batch
  type N and I, the body size of all the individuals was recorded. In the
  batches, S/L, the body size of a subsample of the individuals was recorded.
  Finally, only the body size of the littlest and of the tallest individual was
  recorded. ",
  "Then, (3) we inferred the body size distribution in the S/L and G batches by
  assuming that it followed a normal distribution. The mean and the standard
  deviation were estimated with the measured subsample."
) 
```

@@

During fish sampling, some species are identified based on morphotype but they
belong to the same species based on fecundation criteria (CHECK with Eric).
We merged those morphotype species into one species. There was
`r length(unique(names(sp_to_replace())))` to merge which belonged to 
`r length(unique(sp_to_replace()))` species.

@@

The procedure to obtain altitude, slope, width depth of the streams are fully
explained in main text. Because those measurements were collected during the
fishing protocol, they were easier to manage in the analysis. Then, we detailled
in the following sections how water temperature, flow and BOD were obtained.

@@

Water temperature, flow and BOD (Biogical Oxygen Demand) were obtained from the
[naiades database](http://www.naiades.eaufrance.fr/).
Water temperature, flow and BOD were respectively collected at a hourly, daily
and monthly frequency. Water temperature and flow are recorded by automated
sendors while BOD is collected manually because it necessitates analysis in a
laboratory. BOD data collection is coordinated by the Agence de l'eau which
realized the analysis itself or order it to a company.
It is crucial to make clear that those variables are collected at different
places than the fish samplings.

- Number of station
- Space repartition

```{r, fig.height = 20/2.54}
pca_pressure <- habitat_press
myload(fourier, dir = mypath("data-raw", "polluants"))
myload(flow_temp_metrics, station_analysis, the_8_hydrologic_basin, dir = mypath("data"))
sf_pressure <- station_analysis %>% 
  select(id) %>%
  left_join(rename(pca_pressure, id = station)) %>%
  na.omit()

@@

var_to_plot <- colnames(sf_pressure)[
  !colnames(sf_pressure) %in% c("id", "geometry")]
var_replacement <- c(
  "slope" = "Slope",
  "alt" = "Altitude",
  "d_source" = "Distance from source",
  "strahler" = "Strahler order",
  "width_river_mean" = "Average stream width",
  "avg_depth_station_mean" = "Average stream depth",
  "width_river_cv" = "CV of stream width",
  "avg_depth_station_cv" = "CV of stream depth",
  "DBO_med" = "Average BOD",
  "flow_med" = "Average flow",
  "temperature_med" = "Average temperature",
  "DBO_cv" = "CV of BOD",
  "flow_cv" = "CV of flow",
  "temperature_cv" = "CV of temperature"
)

map_pressure <- map(var_to_plot,
~p +
  geom_sf(data = sf_pressure, aes_string(color = .x)) +
  labs(title = str_replace_all(.x, var_replacement)) +
  theme(legend.title = element_blank(),
    axis.text = element_blank(),
    axis.ticks = element_blank()
  )
)

plot_grid(plotlist = map_pressure, ncol = 2)

```

@@

Several characteristics of the streams make the interpolation more complicated
than along terrestrial surface. Interpolations in terrestrial areas are roughly
based on euclidian distance. Euclidian distance is more complicated to consider
in streams because it had the follow the path of the streams. Futhermore,
two streams can be close by but not connected and the value of their variables
could be not related or a only a few. For those reason, we used stream spatial
network methods to interpolate temperature, flow and BOD.

We reconstructed the stream network and the connection between sites with the
`openSTARS` R package. The reconstruction was done with a raster of digital
elevation model at a resolution of 250 meters [(IGN)](https://wxs.ign.fr/jvam1hsjm11u8voorw81v2xb/telechargement/prepackage/BDALTI-75M_PACK_FXX_2018-01-24%24BDALTIV2_2-0_75M_ASC_LAMB93-IGN69_FRANCE_2018-01-15/file/BDALTIV2_2-0_75M_ASC_LAMB93-IGN69_FRANCE_2018-01-15.7z)
and a theoretical hydrologic network [put a link](test) [@pella_reseau_2012].

The procedure was done by hydrographic basin because of convergence problem
when the interpolation was done at the France scale. We had to make a tradeoff
between the number of data (to keep enough high to perform the interpolation)
and the level of dataset splitting. We then merge some hydrographic basin to end
up with four region of interpolation: West, East, South and North. (XXX ADD 
basins merged)

@@

```{r cv-biais, fig.cap = cv_bias_caption}
cv_dbo_temp_flow %>%
  rename(Bias = bias_avg) %>%
  ggplot(aes(x = Bias)) +
  geom_histogram() +
  facet_wrap(~Variable, scales = "free_x")
```

The performance of the interpolation was evaluated with leave one out
cross-validation (already implemented in the SSN package). The value of the
interpolated variable of each station was predicted after removing it from the
dataset. ADD SUMMARIES ABOUT CV.

With the model, we then simply predicted variable values at the location of the
fish stations.

When predicted values were below the minimum value or above the maximum value
recorded in the dataset for flow, (temperature?) and BOD, we replaced the
predicted value by respectively the minimum and the maximum value found in the
dataset. We ran the interpolation four times and we kept the predicted value
which had the least standard deviation.

@@

```{r sp-list}
myload(species, fish_diet_shift, dir = mypath("data"))
kable(species,
  format = "latex",
  booktabs = T,
  label = paste0("indir-sem"),
  caption = "Fish species list."
  ) %>%
kable_styling(latex_options =c("striped", "scale_down"))

```

```{r food}
kable(fish_diet_shift,
  format = "latex",
  booktabs = T,
  label = paste0("indir-sem"),
  caption = "Ontogenic diet shift for each species"
  ) %>%
kable_styling(latex_options =c("striped", "scale_down"))

```

@@

The CV of biomass over can cover multiple dynamics, including increases,
stable, decreases and a mix of them. Theoretically, however, the CV computed to
quantify stability is often represented with the assumption that the overall
dynamic of the biomass varies around an equilibrium. In order to approach this
condition, we kept only the stations that have met this criteria. To qualify the
biomass trajectories over time, we used the symbolic aggregated approximation
method (SAX) which is commonly used in time series analysis and implemented in
the `jmotif` R package. This method classifies time series rather than
quantifies trends and so is generic enough to encompass the diversity of time
series shapes. The classification necessitates three steps. First, the time
series are normalized (i.e. substracting the mean and divide by the standard
deviation). The second step is to reduce the dimensionality of the time series
by Piecewise Aggregation Approximation (PAA) method. Each time series is divived
in $N$ frames of equal size that allows to the reduce the dimensionality of the
time series. For each frame, we simply kept the mean value of the time series.
The last step is to qualify each frame into string. Because values of
normalized time series typically follows a normal distribution ($N(0,1)$), a
breakpoints can be computed by dividing the area under the normal distribution
in equal parts. The algoritm attributes a alphabetic letter to each part from
the lowest to the highest ($a$, $b$, $c$, ...). We set three breakpoints, so
$a$, $b$ and $c$. Finally, the trajectory of each time series is classified as
a combination of $a$, $b$, $c$ letters. $abc$ and $cba$ time series represent
respectively monoton increasing and decreasing trajectories. For data analysis,
we kept only the $bbb$ which represent time series that showed no temporal
tendancies (with respect to our methodology).

@@

loadings_pca <- matrix(
  as.matrix(round(pca_rotated$rotated$Structure, 2)),
  nrow = 14,
  dimnames = dimnames(pca_rotated$rotated$Structure)
  ) %>%
  as_tibble %>%
  mutate(
    Variable = str_replace_all(
      dimnames(pca_rotated$rotated$Structure)[[1]],
      get_pca_var_name_replacement())
  ) %>%
  select(Variable, RC1, RC2)
kable(
  x = loadings_pca,
  format = "latex",
  booktabs = T,
  label = "contrib-pca",
  caption = caption_contrib_pca
  ) %>%
kable_styling(latex_options = c("striped", "scale_down"))
```

@@

```{r pca-rotated, fig.cap = pca_caption, fig.asp = 1}
p1 <- my_pca_plot(xaxis = "RC1", yaxis = "RC2", ctb_thld = .4)
#p2 <- my_pca_plot(xaxis = "RC3", yaxis = "RC4", ctb_thld = .4)
#p3 <- my_pca_plot(xaxis = "RC4", yaxis = "RC5", ctb_thld = .4)

pca_plot <- plot_grid(p1, eigen_rotated_plot, nrow = 1)
save_plot(
  filename = mypath("manuscript", "bef_stability", "figs", "pca_plot.pdf"),
  pca_plot,
  nrow = 1, ncol = 2,
  base_height = 6/2.54, base_asp = 1, base_width = NULL 
  )
pca_plot
```

@@

```{r rc2-map, fig.cap = caption_rc2_map}
p +
  geom_sf(data = rc2_sf, aes(color = log(value + abs(min(value)) + 1 ))) +
  labs(title = "RC2 (Log)") +
  theme(legend.title = element_blank())
```

@@

```{r}
sem_variable_table <- tibble(
  variable = c(paste0("PCA axis", seq(1, 5)), "Species richness", "Connectance", "Average trophic level", "Synchrony", "CVsp", "Total biomass"),
  unit = c(rep("unitless", 5), "# by square meter", rep("unitless", 4), "gram by square meter"
    ),
  transformation = c(rep("Log base 10", 3), rep("No", 2), "Log base 10", rep("No", 2), rep("Log base 10", 3)),
  interpretation = c(rep("", 11)) 
) %>%
kable(
  format = "latex",
  booktabs = T,
  caption = "Variable description and transformation"
  ) %>%
kable_styling(latex_options = c("striped", "scale_down"))
```

@@

```{r}
hist_var_caption <- paste0(
  "Distribution of the variables (before transformation) used in the Structural Equation Modeling."
)
```
```{r hist-sem-data, fig.cap = hist_var_caption}
sem_data %>%
  select(log_bm_std, log_rich_tot_std, log_sync, log_stab_std, log_cv_sp, log_RC1, log_RC2, t_lvl, ct, log_bm) %>%
  gather(variable, value) %>%
  mutate(variable = str_replace_all(variable, get_sem_var_name_replacement())) %>%
  ggplot(aes(x = value)) +
  geom_histogram() +
  facet_wrap(~variable, scales = "free")
```

@@

```{r s-colin-sem, fig.cap = "Variance Inflation factor for each individual model of stability sem"}

mod_stab_list <-
  list(
    nlme::lme(log_rich_tot_std ~ log_RC1 + log_RC2,  random = ~ 1 | basin, data = sem_data),
    nlme::lme(ct ~ log_RC1 + log_RC2 + log_rich_tot_std, random = ~ 1 | basin, data = sem_data),
    nlme::lme(t_lvl ~ log_RC1 + log_RC2 + log_rich_tot_std, random = ~ 1 | basin, data = sem_data),
    nlme::lme(log_sync ~ log_rich_tot_std + ct + t_lvl + log_RC1 + log_RC2,
      random = ~ 1 | basin, data = sem_data),
    nlme::lme(log_cv_sp ~ log_rich_tot_std  + ct + t_lvl
      + log_RC1 + log_RC2, random = ~ 1 | basin, data = sem_data),
    lm(log_stab_std ~ log_cv_sp + log_sync, data = sem_data),
    nlme::lme(log_bm_std ~ log_rich_tot_std  + ct + t_lvl
      + log_RC1 + log_RC2, random = ~ 1 | basin, data = sem_data)
  )
names(mod_stab_list) <- c(
  "Species richness",
  "Connectance",
  "Avg trophic level",
  "Synchrony",
  "CVsp",
  "Biomass stability",
  "Total biomass"
)

@@

# colinearity table
colin_stab_sem <- tibble(vif = tmp, mod = names(mod_stab_list)) %>%
  unnest(vif) %>%
  mutate(
    value = round(value, 1),
    name = str_replace_all(name, get_sem_var_name_replacement())
    ) %>%
  spread(name, value)

@@

```{r}
caption_mod_res <- paste0(
  "Residuals versus fitted values of the linear models used in the structural
  equation modelings."
) 
```

```{r mod-res, fig.height = 7, fig.cap = caption_mod_res}
library(nlme)
plot_residuals <- function (x, y = "Diagnostic") {
  plot.lme(x, main = y, xlab = "Fitted values", ylab = "Residuals")
}
p_resid_stab_sem <- map2(mod_stab_list, names(mod_stab_list) , plot_residuals)
plot_grid(plotlist = p_resid_stab_sem)
```

@@

  params
}

```

```{r}
est_stab_sem_caption <- paste0(
  "Estimate of the effects for the biomass stability structural equation
  modeling."

@@

```{r}
est_bm_sem_caption <- paste0(
  "Estimate of the effects for the total biomass structural equation
  modeling."
)

@@

```{r}
mask_drop_lm <- names(mod_stab_list) %in% "Biomass stability"
random_coeff_sem <- map(mod_stab_list[!mask_drop_lm], random.effects)

format_random <- function (x, y) {
  tibble(
    Variable = y, 
    `Hydrographic basin` = rownames(x),
    Intercept = x[[1]]
  )
}
formated_random_effects <- do.call(rbind, map2(random_coeff_sem, names(random_coeff_sem), format_random))

caption_random_effect <- paste0(
  "Estimated random effect of hydrographic basin on the intercept of the linear
  models performed in structural equation modeling."

kable(formated_random_effects,
  format = "latex",
  booktabs = T,
  caption = caption_random_effect
  ) %>%
kable_styling(latex_options = c("striped", "scale_down"))
```

@@

```{r sensitivity, fig.dim = c(10, 7), fig.cap = "Sensivity analysis with different dataset", cache = TRUE}
library(furrr)

@@

#myload(network_metrics, dir = mypath("data", "classes"))
sem_sensivity_data <- list(full = op_analysis, bbb = op_analysis_bbb,
  without_holes = op_analysis_wo_holes, bbb_without_holes = op_analysis_wo_holes_bbb)

@@

# Reformat
colnames(sem_stab_results) <- str_to_lower(colnames(sem_stab_results))
sem_stab_results %>%
  mutate(r_p = str_c(response, predictor, sep = "~")) %>%
  ggplot(aes(x = r_p, y = std.estimate)) +
  geom_point(aes(color = dataset)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

@@

# Reformat
colnames(sem_bm_results) <- str_to_lower(colnames(sem_bm_results))
sem_bm_results %>%
  mutate(r_p = str_c(response, predictor, sep = "~")) %>%
  ggplot(aes(x = r_p, y = std.estimate)) +
  geom_point(aes(color = dataset)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

```{r}
knitr::opts_chunk$set(eval = FALSE)
```

>>>>

library(tidyverse)
library(magrittr)
library(ggeffects)
library(cowplot)
library(kableExtra)
library(sf)
source(mypath("R", "misc.R"))
source(mypath("R", "plot_methods.R"))
source(mypath("R", "community_analysis.R"))
source(mypath("R", "community_methods.R"))
source(mypath("R", "statistical_analysis.R"))
source(mypath("R", "total_sem_effect.R"))
source(mypath("R", "press_methods.R"))
source(mypath("R", "geo_methods.R"))
source(mypath("R", "synchrony.R"))
source(mypath("R", "cleaning_methods.R"))

@@

```{r, echo = FALSE}
package <- c("openSTARS", "SSN", "nlme", "piecewiseSEM")
#purrr::map(package, ~ toBibtex(citation(.x)))

#toBibtex(citation())

@@

The fish community sampling took place in a variety of stream size, shape and
depth. This diversity constraints the type of protocol that can take place.  For
the small streams (depth < 0.7m across the entire width), the complete protocol
is used. It consists in placing anodes every X meters across the width of the
river. The fishermen made from one to three row
of fishing. We kept only the first row for analysis to homogenize the sampling
effort. For deeper and wider streams, the sampling was partial over the bank and
the channel and performed by boat and by foot (along the bank). We kept only
sampling done over the bank because channel sampling was not always done. Two
types of partial protocols takes place: partial over bank and partial by points.
The former is continuous while the latter is discrete. Furthermore, in partial
by point protocol the channel can be sampled as well. We kept only the partial
by point fish sampling which all the sampling point were done over the bank to
homogenize the sampling. Then, we merged partial over bank and partial over
point protocols. Some sampling stations had mix characteristics in which mix of
partial and complete protocols were applied depending of the depth of the river
at the time of sampling.

Heterogeneity in the sampling period may introduce variability that is not related
to ecological processes such as the presence of juveniles. In order to reduce
heterogeneity in sampling time, only one sampling per year was retained if there
was two in a given year, the one with with the most species and then individual
collected. Finally, most of the fish sampling occurred in September (Median:
mid-August) and the median standard deviation of the sampling month was inferior
to one (0.7) within station. Additionally, we removed sampling events, in a
given station, which the sampled length along the stream was outside the median
length sampled more or less 30%. Finally, we standardized the biomass record
and species richness by the sampled surface to get rid of sampling effort
effects.

@@

During the electric fishing, and before that fish body size are measured, they
are regrouped by batches. Each batches contains one species but there can be
several batches by species. Body size assessment are different according to the
batches. There are four types of batches: N, I, S/L and G. The batches N and
I contains the biggest individuals, there are normally less numerous and then
the body size of the individuals of those batches is recorded. The batches S/L
contains fishes of intermediate sizes. Inside each S/L batches, the operator
tries to make batches as homogeneous as possible in body size. Then, the body
size of a subsample of X individuals are recorded. The G batches contain
individuals of low body size, with care that body size is as homogeneous as
possible in the batches. Then body size of the shortest and the longest
individuals are recorded.

@@

```{r}
body_size_caption <- paste0(
  "Body size inference of the fishes. ",
  "(1) Sampled fishes were attributed to batch type according to their size and
  the number of individuals. A batch contains one species only. (2) In the batch
  type N and I, the body size of all the individuals was recorded. In the
  batches, S/L, the body size of a subsample of the individuals was recorded.
  Finally, only the body size of the littlest and of the tallest individual was
  recorded in the G batches. ",
  "Then, (3) we inferred the body size distribution in the S/L and G batches by
  assuming that it followed a normal distribution. The mean and the standard
  deviation were estimated with the measured subsample."
) 
```

@@

During fish sampling, some species are identified based on morphotype but they
belong to the same species based on fecundation criteria.
We merged those morphotype species into one species. There was
`r length(unique(names(sp_to_replace())))` to merge which belonged to 
`r length(unique(sp_to_replace()))` species.

@@

The procedure to obtain altitude, slope, width depth of the streams are fully
explained in main text. Because those measurements were collected during the
fishing protocol, they were easier to manage in the analysis. Then, we detailed
in the following sections how water temperature, flow and BOD were obtained.

@@

Water temperature, flow and BOD (Biological Oxygen Demand) were obtained from the
[naiades database](http://www.naiades.eaufrance.fr/).
Water temperature, flow and BOD were respectively collected at a hourly, daily
and monthly frequency. Water temperature and flow are recorded by automated
sensors while BOD is collected manually because it necessitates analysis in a
laboratory. BOD data collection is coordinated by the Agence de l'eau which
realized the analysis itself or order it to a company.
It is crucial to make clear that those variables are collected at different
places than the fish samplings.

```{r}
pressure_cap <- paste0(
  "Map of environmental variables obtained for the 99 sites used in the analysis."
)
```

```{r, fig.height = 20/2.54}
pca_pressure <- habitat_press
myload(fourier, dir = mypath("data-raw", "polluants"))
myload(flow_temp_metrics, station_analysis, the_8_hydrologic_basin, dir = mypath("data"))

sf_pressure <- station_analysis %>% 
  filter(id %in% op_analysis_bbb$station) %>%
  select(id) %>%
  left_join(rename(pca_pressure, id = station)) %>%
  na.omit()

@@

var_to_plot <- colnames(pca_rotated$normal$tab)

var_replacement <- c(
  "slope" = "Slope",
  "alt" = "Altitude",
  "d_source" = "Distance from source",
  "strahler" = "Strahler order",
  "width_river_mean" = "Average stream width",
  "avg_depth_station_mean" = "Average stream depth",
  "width_river_cv" = "CV of stream width",
  "avg_depth_station_cv" = "CV of stream depth",
  "DBO_med" = "Average BOD",
  "flow_med" = "Average flow",
  "temperature_med" = "Average temperature",
  "DBO_cv" = "CV of BOD",
  "flow_cv" = "CV of flow",
  "temperature_cv" = "CV of temperature"
)

map_pressure <- map(var_to_plot,
~p +
  geom_sf(data = sf_pressure, aes_string(color = .x), size = .5) +
  viridis::scale_color_viridis() +
  labs(title = str_replace_all(.x, var_replacement)) +
  theme(legend.title = element_blank(),
    text = element_text(size = 8),
    axis.text = element_blank(),
    axis.ticks = element_blank()
  ) +
 guides(fill = guide_colourbar(barwidth = 0.5, barheight = 10))
)

plot_grid(plotlist = map_pressure, ncol = 3)
```

@@

Several characteristics of the streams make the interpolation more complicated
than along terrestrial surface. Interpolations in terrestrial areas are roughly
based on euclidean distance. Euclidean distance is more complicated to consider
in streams because it had the follow the path of the streams. Furthermore,
two streams can be close by but not connected and the value of their variables
could be not related or a only a few. For those reason, we used stream spatial
network methods to interpolate temperature, flow and BOD.

We reconstructed the stream network and the connection between sites with the
`openSTARS` R package. The reconstruction was done with a raster of digital
elevation model at a resolution of 250 meters [(IGN)](https://wxs.ign.fr/jvam1hsjm11u8voorw81v2xb/telechargement/prepackage/BDALTI-75M_PACK_FXX_2018-01-24%24BDALTIV2_2-0_75M_ASC_LAMB93-IGN69_FRANCE_2018-01-15/file/BDALTIV2_2-0_75M_ASC_LAMB93-IGN69_FRANCE_2018-01-15.7z)
and a theoretical hydrologic network [@pella_reseau_2012].

The procedure was done by hydrographic basin because of convergence problem
when the interpolation was done at the France scale. We had to make a trade-off
between the number of data (to keep enough high to perform the interpolation)
and the level of dataset splitting. We then merge some hydrographic basin to end
up with four region of interpolation: West, East, South and North. (XXX ADD 
basins merged)

@@

The performance of the interpolation was evaluated with leave one out
cross-validation (already implemented in the SSN package). The value of the
interpolated variable of each station was predicted after removing it from the
dataset.

When predicted values were below the minimum value or above the maximum value
recorded in the dataset for flow, temperature and BOD, we replaced the
predicted value by respectively the minimum and the maximum value found in the
dataset. We ran the interpolation four times and we kept the predicted value
which had the least standard deviation.

@@

```{r sp-list}
myload(species, fish_diet_shift, dir = mypath("data"))
kable(species,
  format = "latex",
  booktabs = T,
  label = paste0("fish-sp"),
  caption = "Fish species list."
  ) %>%
kable_styling(latex_options =c("striped"))
```

```{r food}
kable(select(fish_diet_shift, - species_name, -remark),
  format = "latex",
  booktabs = T,
  label = paste0("onto-diet"),
  caption = "Ontogenic diet shift for each species"
  ) %>%
kable_styling(latex_options =c("striped", "scale_down"))
```

@@

The CV of biomass over can cover multiple dynamics, including increases,
stable, decreases and a mix of them. Theoretically, however, the CV computed to
quantify stability is often represented with the assumption that the overall
dynamic of the biomass varies around an equilibrium. In order to approach this
condition, we kept only the stations that have met this criteria. To qualify the
biomass trajectories over time, we used the symbolic aggregated approximation
method (SAX) which is commonly used in time series analysis and implemented in
the `jmotif` R package. This method classifies time series rather than
quantifies trends and so is generic enough to encompass the diversity of time
series shapes. The classification necessitates three steps. First, the time
series are normalized (i.e. Substituting the mean and divide by the standard
deviation). The second step is to reduce the dimensionality of the time series
by Piecewise Aggregation Approximation (PAA) method. Each time series is divided
in $N$ frames of equal size that allows to the reduce the dimensionality of the
time series. For each frame, we simply kept the mean value of the time series.
The last step is to qualify each frame into string. Because values of
normalized time series typically follows a normal distribution ($N(0,1)$), a
breakpoints can be computed by dividing the area under the normal distribution
in equal parts. The algorithm attributes a alphabetic letter to each part from
the lowest to the highest ($a$, $b$, $c$, ...). We set three breakpoints, so
$a$, $b$ and $c$. Finally, the trajectory of each time series is classified as
a combination of $a$, $b$, $c$ letters. $abc$ and $cba$ time series represent
respectively monotonic increasing and decreasing trajectories. For data analysis,
we kept only the $bbb$ which represent time series that showed no temporal
tendencies, with respect to our methodology.

@@

loadings_pca <- matrix(
  as.matrix(round(pca_rotated$rotated$Structure, 2)),
  nrow = 14,
  dimnames = dimnames(pca_rotated$rotated$Structure)
  ) %>%
  as_tibble %>%
  mutate(
    Variable = str_replace_all(
      dimnames(pca_rotated$rotated$Structure)[[1]],
      get_pca_var_name_replacement())
  ) %>%
  select(Variable, RC1, RC2)
kable(
  x = loadings_pca,
  format = "latex",
  booktabs = T,
  label = "contrib-pca",
  caption = caption_contrib_pca
  ) %>%
kable_styling(latex_options = c("striped"))
```

@@

```{r pca-rotated, fig.cap = pca_caption}
p1 <- my_pca_plot(xaxis = "RC1", yaxis = "RC2", ctb_thld = .4)
#p2 <- my_pca_plot(xaxis = "RC3", yaxis = "RC4", ctb_thld = .4)
#p3 <- my_pca_plot(xaxis = "RC4", yaxis = "RC5", ctb_thld = .4)

pca_plot <- plot_grid(p1, eigen_rotated_plot, nrow = 1)
save_plot(
  filename = mypath("manuscript", "bef_stability", "figs", "pca_plot.pdf"),
  pca_plot,
  nrow = 1, ncol = 2,
  base_height = 6/2.54, base_asp = 1.6, base_width = NULL 
  )
pca_plot
```

@@

```{r rc2-map, fig.cap = caption_rc2_map}
p +
  geom_sf(data = rc2_sf, aes(color = log(value + abs(min(value)) + 1 ))) +
  viridis::scale_color_viridis() +
  labs(title = "RC2 (Log)") +
  theme(legend.title = element_blank())
```

@@

```{r}
sem_variable_table <- tibble(
  variable = c(paste0("PCA axis", seq(1, 5)), "Species richness", "Connectance", "Average trophic level", "Synchrony", "CVsp", "Total biomass"),
  unit = c(rep("unitless", 5), "# by square meter", rep("unitless", 4), "gram by square meter"
    ),
  transformation = c(rep("Log base 10", 3), rep("No", 2), "Log base 10", rep("No", 2), rep("Log base 10", 3)),
  interpretation = c(rep("", 11)) 
) %>%
kable(
  format = "latex",
  booktabs = T,
  caption = "Variable description and transformation"
  ) %>%
kable_styling(latex_options = c("striped", "scale_down"))
sem_variable_table
```

@@

```{r}
hist_var_caption <- paste0(
  "Distribution of the variables used in the Structural Equation Modeling. The
  biomass stability, the CV of species (CVsp), PCA1, PCA2, species richness,
  synchrony and total biomass were logged."
)
```

```{r hist-sem-data, fig.cap = hist_var_caption}
sem_data %>%
  select(log_bm_std, log_rich_tot_std, log_sync, log_stab_std, log_cv_sp, log_RC1, log_RC2, t_lvl, ct) %>%
  gather(variable, value) %>%
  mutate(variable = str_replace_all(variable, get_sem_var_name_replacement())) %>%
  ggplot(aes(x = value)) +
  geom_histogram() +
  facet_wrap(~variable, scales = "free")
```

@@

```{r}
colin_sem_cap <- paste0(
  "Variance Inflation Factor for each individual linear model of the structural
  equation models."
) 
```

```{r s-colin-sem, fig.cap = ""}
mod_stab_list <-
  list(
    nlme::lme(log_rich_tot_std ~ log_RC1 + log_RC2,  random = ~ 1 | basin, data = sem_data),
    nlme::lme(ct ~ log_RC1 + log_RC2 + log_rich_tot_std, random = ~ 1 | basin, data = sem_data),
    nlme::lme(t_lvl ~ log_RC1 + log_RC2 + log_rich_tot_std, random = ~ 1 | basin, data = sem_data),
    nlme::lme(log_sync ~ log_rich_tot_std + ct + t_lvl + log_RC1 + log_RC2,
      random = ~ 1 | basin, data = sem_data),
    nlme::lme(log_cv_sp ~ log_rich_tot_std  + ct + t_lvl
      + log_RC1 + log_RC2, random = ~ 1 | basin, data = sem_data),
    lm(log_stab_std ~ log_cv_sp + log_sync, data = sem_data),
    nlme::lme(log_bm_std ~ log_rich_tot_std  + ct + t_lvl
      + log_RC1 + log_RC2, random = ~ 1 | basin, data = sem_data)
  )
names(mod_stab_list) <- c(
  "Species richness",
  "Connectance",
  "Avg trophic level",
  "Synchrony",
  "CVsp",
  "Biomass stability",
  "Total biomass"
)

@@

# colinearity table
colin_stab_sem <- tibble(vif = tmp, mod = names(mod_stab_list)) %>%
  unnest(vif) %>%
  rename(`Response variable` = mod) %>%
  mutate(
    value = round(value, 1),
    name = str_replace_all(name, get_sem_var_name_replacement())
    ) %>%
  spread(name, value)

@@

```{r}
caption_mod_res <- paste0(
  "Residuals versus fitted values of the linear models used in the structural
  equation models."
) 
```

```{r mod-res, fig.height = 8, fig.cap = caption_mod_res}
library(nlme)
plot_residuals <- function (x, y = "Diagnostic") {
  plot.lme(x, main = y, xlab = "Fitted values", ylab = "Residuals")
}
p_resid_stab_sem <- map2(mod_stab_list, names(mod_stab_list) , plot_residuals)
plot_grid(plotlist = p_resid_stab_sem, ncol = 2)
```

@@

  params
}
```

```{r}
est_stab_sem_caption <- paste0(
  "Estimate of the effects for the temporal stability of annual biomass of the structural equation
  model."

@@

```{r}
est_bm_sem_caption <- paste0(
  "Estimate of the effects for the structural equation
  model of the median of annual total biomass."
)

@@

```{r}
mask_drop_lm <- names(mod_stab_list) %in% "Biomass stability"
random_coeff_sem <- map(mod_stab_list[!mask_drop_lm], random.effects)
test <- getVarCov(mod_stab_list[!mask_drop_lm][[2]])

get_intercept_variance <- function (mod) {
  vc <- VarCorr(mod)
  suppressWarnings(storage.mode(vc) <- "numeric")
  enframe(vc[1,])
}
random_coeff_sem <- map(mod_stab_list[!mask_drop_lm],
  get_intercept_variance) %>%
  enframe(name = "variable") %>%
  unnest(value) %>%
  pivot_wider(names_from = "name", values_from = "value")
get_intercept <- function (mod) {
  mod[["coefficients"]]$fixed["(Intercept)"]
}
intercept_sem <- map_dbl(mod_stab_list[!mask_drop_lm],
  get_intercept) %>%
enframe(name = "variable", value = "Intercept")

formated_random_effects <- intercept_sem %>% 
  left_join(random_coeff_sem, by = "variable") %>%
  rename(`Response variable` = variable)
#format_random <- function (x, y) {
  #tibble(
    #Variable = y, 
    #`Hydrographic basin` = rownames(x),
    #Intercept = x[[1]]
  #)
#}
#formated_random_effects <- do.call(rbind, map2(random_coeff_sem, names(random_coeff_sem), format_random))

caption_random_effect <- paste0(
  "Estimated random effect of hydrographic basin on the intercept of the linear
  models performed in structural equation modeling."
)

kable(formated_random_effects,
  format = "latex",
  booktabs = T,
  caption = caption_random_effect
  ) %>%
kable_styling(latex_options = c("striped"))
```

@@

```{r sensitivity, message = FALSE, fig.dim = c(10, 7), fig.cap = "Sensivity analysis with different dataset", cache = FALSE}
library(furrr)

@@

myload(network_metrics, dir = mypath("data", "classes"))
sem_sensivity_data <- list(full = op_analysis, bbb = op_analysis_bbb,
  without_holes = op_analysis_wo_holes, bbb_without_holes = op_analysis_wo_holes_bbb)

@@

# Reformat
colnames(sem_stab_results) <- str_to_lower(colnames(sem_stab_results))
mysave(sem_stab_results, dir = mypath("data"), overwrite = TRUE)
```

@@

# Reformat
colnames(sem_bm_results) <- str_to_lower(colnames(sem_bm_results))
mysave(sem_bm_results, dir = mypath("data"), overwrite = TRUE)
```
